---
title: "Iteration and ListCols"
author: "Mahdi Maktabi"
date: "2024-10-29"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
```


## Here's some lists

```{r}
l = list(
  vec_numeric = 1:4,
  unif_sample = runif(100),
  mat = matrix(1:8, nrow = 2, ncol = 4, byrow = TRUE),
  summary = summary(rnorm(100))
)

l$mat

l[["mat"]][1:3]

l[[1]]
l[[4]]
```

Make a list that's hopefully a it more useful.

```{r}
list_norm =
  list(
    a = rnorm(20, 0, 5),
    b = rnorm(20, 4, 5),
    c = rnorm(20, 0, 10),
    d = rnorm(20, 4, 10)
  )

list_norm[["a"]]
```

Let's reuse a function we wrote last time.

```{r}
mean_and_sd = function(x) {
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  out_df =
    tibble(
      mean = mean_x,
      sd = sd_x
    )
  
  return(out_df)
}
```

Lets use this function to take mean and sd of all samples.

```{r}
mean_and_sd(list_norm[["a"]])
mean_and_sd(list_norm[["b"]])
mean_and_sd(list_norm[["c"]])
mean_and_sd(list_norm[["d"]])
```

## Use a for loop

Create output list, and run a for loop.

```{r}
output = vector("list", length = 4)

for (i in 1:4) {
  
  output[[i]] = mean_and_sd(list_norm[[i]])
  
}
```


## Do the same thing

but with 'map' instead.

```{r}
output = map(list_norm, mean_and_sd)
```

Let's do a couple of other things.

```{r}
output = map(list_norm, median)

output = map(list_norm, IQR)

output = map_dbl(list_norm, median)

output = map_dfr(list_norm, median)

output =
  map(list_norm, mean_and_sd) |> 
  bind_rows()
```



## LIST COLUMNS!!

```{r}
listcol_df = 
  tibble(
    name = c("a", "b", "c", "d"),
    samp = list_norm
  )

listcol_df

listcol_df |> 
  filter(name %in% c("a", "b"))

listcol_df |> 
  select(-samp)
```

```{r}
listcol_df[["samp"]]["a"]
```

Compute mean and sd

```{r}
mean_and_sd(listcol_df[["samp"]][["a"]])


map(listcol_df[["samp"]], mean_and_sd)
```

Add a list column

```{r}
listcol_df |> 
  mutate(
    output = map(samp, mean_and_sd), #map will return in list format
    iqr = map_dbl(samp, IQR)) #map_dbl will make it directly an output

listcol_df |> 
  mutate(
    output = map(samp, mean_and_sd),
    iqr = map_dbl(samp, IQR)) |> 
  select(-samp) |> 
  unnest(output) #Takes that nested df and expands it into columns.
```


### NSDUH Dataset

This is our version of the dataset from last time.

```{r}
nsduh_import = function(html, number) {
  
  drug_table =
    html |> 
    html_table() |> 
    nth(number) |> 
    slice(-1) |> 
    select(-contains("P Value"))
  
  return(drug_table)
  
} 
```

We need to import the html, and then extract the correct table.

```{r}
nsduh_url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"

nsduh_html = read_html(nsduh_url)
```

```{r}
nsduh_import(html = nsduh_html, number = 1)
nsduh_import(html = nsduh_html, number = 4)
nsduh_import(html = nsduh_html, number = 5)
```

```{r}
nsduh_df =
  tibble(
    drug = c("marj", "cocaine", "heroin"),
    number = c(1, 4, 5)
  ) |> 
  mutate(table = map(number, \(num) nsduh_import(html = nsduh_html, num))) |> 
  unnest(table)
```

